Comparing probabilistic accounts of probability judgments

### 2021-09-24 paper-rmd/paper-papaja.Rmd
updates to plots

t1_df %>% 
  select(-X1) %>% 
  mutate(model = gsub("BS", "Bayesian Sampler", model)) %>% 
  rename(Model = model) %>% 
  kbl(caption="Original model fitting results", digits=1, booktabs=T) %>% 
  kable_classic(full_width=F) %>% 
  row_spec(1, bold=TRUE)
```

@@

\begin{figure}
  \begin{minipage}{.5\textwidth}
    \flushright
    \input{ptn_platediagram}
  \end{minipage}%
  \begin{minipage}{.5\textwidth}
    \flushleft
    \small
    \begin{align}
      y_{ijk} &\sim beta\big(\mu_{ijk} \kappa, (1-\mu_{ijk}) \kappa \big) \\
      \mu_{ijk} &= f_{PT+N}(\overrightarrow{p_{jk}}, d_j, d_j)  \\
      d_j &= \frac{expit(\delta_j)}{2} \\
      d_j’ &= \frac{expit\big(\delta_j + \exp(\Delta\delta_j)\big)}{2} \\
      \overrightarrow{p_{jk}} &\sim Dirichlet(\overrightarrow{1}) \\
      \delta_j &\sim Normal(0,1) \\
      \Delta\delta_j &\sim Normal(0,1) \\
      \kappa &\sim HalfCauchy(20)
    \end{align}
  \end{minipage}
  \caption{Complex unpooled PT+N model diagram and formula specifications. Circular nodes are parameters, shaded nodes are observations, and squared nodes are deterministic functions of parameters. Plates signify values defined for $i$ trials, $j$ participants, and $k$ conditions.}
\end{figure}

@@

t2_df %>% 
  select(-X1) %>% 
  gather(measure, value, -Experiment, -model) %>% 
  pivot_wider(names_from = c(Experiment, measure), values_from=value,names_sort = T) %>% 
  rename(Model = model) %>%
  kbl(
    caption="Bayesian model comparison results", 
    digits=3, 
    booktabs=T,
    col.names = c("Model", "$LOO_{ic}$", "Penalty","$r_{resp}$", "$r_{trial}$", "$LOO_{ic}$", "Penalty","$r_{resp}$", "$r_{trial}$"),
    escape = F
    ) %>%
  add_header_above(c(" ", "Experiment 1"=4, "Experiment 2"=4)) %>% 
  kable_classic(full_width=F) %>% 
  kable_styling(latex_options="scale_down") %>% 
  row_spec(1, bold=TRUE)
```

>>>>

t1_df %>% 
  select(-`...1`) %>% 
  mutate(model = gsub("BS", "Bayesian Sampler", model)) %>% 
  rename(Model = model) %>% 
  kbl(caption="Original model fitting results", digits=1, booktabs=T) %>% 
  kable_classic(full_width=F) %>% 
  row_spec(1, bold=TRUE)
```

@@

\begin{figure}
  \begin{minipage}{.5\textwidth}
    \flushright
    \input{ptn_platediagram}
  \end{minipage}%
  \begin{minipage}{.5\textwidth}
    \flushleft
    \small
    \begin{align*}
      y_{ijk} &\sim beta\big(\mu_{ijk} \kappa, (1-\mu_{ijk}) \kappa \big) \\
      \mu_{ijk} &= f_{PT+N}(\overrightarrow{p_{jk}}, d_j, d_j)  \\
      d_j &= \frac{expit(\delta_j)}{2} \\
      d_j’ &= \frac{expit\big(\delta_j + \exp(\Delta\delta_j)\big)}{2} \\
      \overrightarrow{p_{jk}} &\sim Dirichlet(\overrightarrow{1}) \\
      \delta_j &\sim Normal(0,1) \\
      \Delta\delta_j &\sim Normal(0,1) \\
      \kappa &\sim HalfCauchy(20)
    \end{align*}
  \end{minipage}
  \caption{Complex unpooled PT+N model diagram and formula specifications. Circular nodes are parameters, shaded nodes are observations, and squared nodes are deterministic functions of parameters. Plates signify values defined for $i$ trials, $j$ participants, and $k$ conditions.}
\end{figure}

@@

t2_df %>% 
  select(-`...1`) %>% 
  gather(measure, value, -Experiment, -model) %>% 
  pivot_wider(names_from = c(Experiment, measure), values_from=value,names_sort = T) %>% 
  rename(Model = model) %>%
  kbl(
    caption="Bayesian model comparison results", 
    digits=3, 
    booktabs=T,
    col.names = c("Model", "$LOO_{ic}$", "Penalty","$r_{resp}$", "$r_{trial}$", "$LOO_{ic}$", "Penalty","$r_{resp}$", "$r_{trial}$"),
    escape = F
    ) %>%
  add_header_above(c(" ", "Experiment 1"=4, "Experiment 2"=4)) %>% 
  kable_classic(full_width=F) %>% 
  kable_styling(latex_options="scale_down") %>% 
  row_spec(1, bold=TRUE)
```
